Taking from the rich or giving to the poor: Evidence for a two-dimension measure of support for redistribution

### 2018-08-21 analysis/manuscript.Rmd
Ammending typo

behaviour---
title: "Taking from the rich or giving to the poor: Evidence for a two-dimension measure of support for redistribution"
date: "`r Sys.Date()`"
output:
  workflowr::wflow_html:
    toc: false
---

>>>>

---
title: "Taking from the rich or giving to the poor: Evidence for a two-dimension measure of support for redistribution"
date: "`r Sys.Date()`"
output:
  workflowr::wflow_html:
    toc: false
---
